Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-30 main_new.tex
updates

Based on the Gaussian modeling assumptions, the EPs in Eq. (\ref{eq:prob}) can be computed at any location $\bx$. Without additional data, we have
\begin{eqnarray}\label{eq:prob_mv0}
 p(\bx) &=& P(\xi_a(\bx) \leq T_a, \xi_b(\bx) \leq T_b) \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} T_a\\
T_b
\end{bmatrix};
\begin{bmatrix} \mu_{a}(\bx)\\
\mu_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
\sigma_{a}^2(\bx) & \sigma_{a}(\bx)\sigma_{b}(\bx) \gamma  \\
\sigma_{a}(\bx)\sigma_{b}(\bx) \gamma  & \sigma_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
where $\Phi_2$ is the bivariate Gaussian cumulative distribution function, and the mean and covariance entries are defined in Eq. (\ref{gp_bar}).

When data $\by$ is available, we similarly get
\begin{eqnarray}\label{eq:prob_mv}
 p(\bx;\by) &=& P(\xi_a(\bx) \leq T_a, \xi_b(\bx) \leq T_b |\by) 
 \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} T_a\\
T_b
\end{bmatrix};
\begin{bmatrix} m_{a}(\bx)\\
m_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
s_{a}^2(\bx) & s_{a,b}(\bx)  \\
s_{a,b}(\bx)  & s_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
with parameters defined in Eq. (\ref{gp_upd}) and (\ref{gp_hat}).

For one particular dataset, the probability $p(\bx;\by)$ can be closer to $0.5$ than the initial probability $p(\bx)$. This means that the variance in the ES is increased. On average, taking expectations over the data $\by$, the ES variance will be reduced by gathering data. We next explain how AUVs can be used to efficiently gather data and reduce the overall marginal spatial uncertainties in the ES.

>>>>

Based on the Gaussian modeling assumptions, the EPs in Eq.
(\ref{eq:prob}) can be computed at any location $\bx$. Without
additional data, we have:

\begin{eqnarray}\label{eq:prob_mv0}
 p(\bx) &=& P(\xi_a(\bx) \leq T_a, \xi_b(\bx) \leq T_b) \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} T_a\\
T_b
\end{bmatrix};
\begin{bmatrix} \mu_{a}(\bx)\\
\mu_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
\sigma_{a}^2(\bx) & \sigma_{a}(\bx)\sigma_{b}(\bx) \gamma  \\
\sigma_{a}(\bx)\sigma_{b}(\bx) \gamma  & \sigma_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}

where $\Phi_2$ is the bivariate Gaussian cumulative distribution
function, and the mean and covariance entries are as defined in Eq.
(\ref{gp_bar}).

When $\by$ is available, we similarly get:

\begin{eqnarray}\label{eq:prob_mv}
 p(\bx;\by) &=& P(\xi_a(\bx) \leq T_a, \xi_b(\bx) \leq T_b |\by) 
 \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} T_a\\
T_b
\end{bmatrix};
\begin{bmatrix} m_{a}(\bx)\\
m_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
s_{a}^2(\bx) & s_{a,b}(\bx)  \\
s_{a,b}(\bx)  & s_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}

with parameters as defined in Eq. (\ref{gp_upd}) and (\ref{gp_hat}).

For one particular dataset \kcomment{This is unclear, rephrase}, the
probability $p(\bx;\by)$ can be closer to $0.5$ than the initial
probability $p(\bx)$. This means that the variance in the ES is
increased. On average, taking expectations over the data $\by$, the ES
variance will be reduced by gathering data. We next explain how AUVs
can be used to efficiently gather data and reduce the overall marginal
spatial uncertainties in the ES.
